
% -------------------------------------------------------------
%    Implementation
% -------------------------------------------------------------

\section{Implementation}
\subsection{Implementation Frontend}

\subsection{Implenemtation Backend}

The core algorithm of the application is the Optimization-process, which calculates, based on given Data from the Asset Manager
and the Source Data Manager, the most optimal time schedule for the production units, with focus on the most cost-efficient outcome. 
Those calculations are affected by the choice of Scenarios and the maintenance of the production unit. 

\subsubsection*{Data from Asset Manager}

For the calculation of the time schedule, first the Scenario Manager provides a list of Generic units for the Asset Manager.
The Asset Manager passes the list to the GenericToOptimizedAdapter, which identifies each unit in the given list as one of three
types of units:  HybridUnit, ElectricUnit or CombustionUnit. And creates a new list with the identified units. 
This list gets passed back to the Asset Manager, which provides it for the Optimizer request.  

\subsubsection*{Data from Source Data Manager}

Next to the list of units the Optimizer also depends on the Data of the heat demand, and for the second scenario the
electricity prices, as well as the current period, summer or winter. 
Those Data get provided by the Source Data Manager, which first loads Data from a given from the Source Data Loader 
in form of Time series objects. These Objects contain a Date and time, the period and the value for the heat demand 
or the value for the electricity price and can be indexed by the DateTime value. The Source Data Manager contains two
functions, one to load the electricity price and one to load the heat demand. Those functions get called by the 
Optimizer to obtain the required Data for the calculation. 

\subsubsection*{Calculation for Optimization}

For the optimization process the Optimizer contains a function that first calculates the value of heat per price for
each available unit and adds it to the unit’s properties as HeatPerPriceRecords. 
With these values the next function sorts through the list of available units and sorts for the HeatPerPriceRecords 
value, form most heat per cost to least money. It also calculates if the Unit can produce the required heat demand on 
its own or if additional units are required, by comparing the heat demand to the maximum of heat the unit can produce. 

\subsubsection*{Optimization function}

In the optimize function itself, the application calculates heat per price and sorts the list of available units for
each hour in the selected duration. 
The optimization function gets called when the Result Data Manger requests the optimized data. 

\subsubsection*{ResultDataManager}

After calling the optimized data from the Optimizer, the Result Data Manager adds the number of used hours for each 
unit and safes the Data as CSV file. 
Those Data can be requested by the Data Visualizer. 

\subsubsection*{Maintenance}

The Optimizer Class contains a function that sets a selected unit on maintenance for a chosen number of hours. The 
start of the maintenance will be selected randomly by the program and is only possible during summer period due to 
less heat demand. 
During the sorting process, of the available units the function checks if each unit is on maintenance, if its true 
the loop continues with the next unit of the list and doesn’t add the maintenance unit to the optimized list. 

\subsection{Implementation Data Management}