% -------------------------------------------------------------
% Process-related problem
% -------------------------------------------------------------
\noindent Suggested length is 7 – 10 pages

\section{How to set tables in \LaTeX?}

\hl{Now lets add a table that looks good}. For the relevant data please see Table~\ref{tab:nicetable}.

\begin{table}[htbp]
  \centering
  \caption[This is the short table caption]{This is a very long table caption, with lots of information and interesting facts.}
  \label{tab:nicetable}
  \begin{tabular}{lcr}  \toprule   % l-left, c-centre, r-right
      \multicolumn{2}{c}{Group text add}            \\ \cmidrule(r){1-2}
      Property \hspace{35mm}      & Units    & Value   \\ \midrule
      Young's modulus  & MPa      & $2.10\times 10^5$  \\ 
      Density          & kg/m$^3$ & 7,830              \\
      Ultimate stress  & MPa      & 235.0              \\
      Young's modulus  & MPa      & $2.10\times 10^5$  \\
      Density          & kg/m$^3$ & 7,830              \\
      Ultimate stress  & MPa      & 235.0              \\
      Colour           & $-$      & Blue               \\ \bottomrule
  \end{tabular}
\end{table}

\section{Problem Statement}

\begin{itemize}

    \item [-] Provide background information on the selected process-related problem.
    \item [-] Justify why addressing this problem is important for your team and in general, e.g., efficiency, project success, and future professional work and development.
    \item [-] Formulate a clear and well-defined problem statement.
  
\end{itemize}

\section{Selected Solution}

\begin{itemize}

    \item [-] Introduce the Scrum practice(s) (or the whole Scrum framework) chosen to address the problem.
    \item [-] Justify why this practice(s) or the Scrum framework was selected and how it aligns with solving the issue.
    \item [-] Support the discussion with references to Scrum literature or Agile best practices. You could also support your claims from your own experiences, e.g., past semester projects.

\end{itemize}

\section{Implementation}

\begin{itemize}

    \item [-] Describe how the selected Scrum practice(s) were applied in the project.
    \item [-] Provide empirical evidence (e.g., Scrum board snapshots, Sprint Review sessions transcripts, etc.).
    \item [-] Explain how the team adapted the approach to fit their project context.

\end{itemize}

\section{Results}

\begin{itemize}

    \item [-] Analyze to what extent the solution alleviated the problem.
    \item [-] Provide qualitative and/or quantitative evidence (e.g., sprint velocity improvements, better team coordination).
    \item [-] Discuss any challenges encountered and how they were mitigated.

\end{itemize}