%----------------------------------------------------------------------------------------
%	Software Engineering-related problem
%----------------------------------------------------------------------------------------
\noindent Follow the same structure as the Process-Related Problem section but applied to the SE-related problem. Suggested length is 7 – 10 pages

\section{Problem Statement}

\begin{itemize}

    \item [-] Introduce and justify the selected SE-related problem.
    \item [-] Explain how it impacts software development of an aspect(s) of the software product, e.g., software quality, maintainability, performance, etc.
  
\end{itemize}

\section{Selected Solution}

\begin{itemize}

    \item [-] Identify the Software Engineering (SE) practice, technique, or principle chosen to address the issue.
    \item [-] This must be based on a SWEBOK Knowledge Area (KA) or a course topic (e.g., TDD, DevOps, Software Quality, Requirements Engineering).
    \item [-] Justify why this solution is a good fit for the problem.

\end{itemize}


\section{Implementation}

\begin{itemize}

    \item [-] Describe how the solution was applied in the project.
    \item [-] Provide empirical evidence (e.g., improved code quality (code snippets before and after), test results, UML diagrams).
    \item [-] Explain how the team adapted and iterated on the solution.
    
\end{itemize}

\section{Results}

\begin{itemize}

    \item [-] Evaluate to what extent the solution mitigated, improved, or addressed the problem.
    \item [-] Provide evidence of success achieved (if any) and challenges faced.
    \item [-] Discuss any potential improvements if the solution were to be used again.

\end{itemize}